---
title: "Fair or Foul"
author: "Israel Miller"
date: "5/15/19"
output:
  pdf_document: default

---

<!-- For more info on RMarkdown see http://rmarkdown.rstudio.com/ -->

<!-- Enter the code required to load your data in the space below. The data will be loaded but the line of code won't show up in your write up (echo=FALSE) in order to save space-->
```{r echo=FALSE, cache=TRUE, include=FALSE}
#Load your data here
library(tidyverse)
events <- read_csv("data/events.csv") %>% mutate_if(is.character, factor)
matchdetails <- read_csv("data/matchdetails.csv") %>% mutate_if(is.character, factor)
teams <- read_csv("data/teams.csv") %>% mutate_if(is.character, factor)


```

<!-- In the remainder of the document, add R code chunks as needed -->

### Introduction:

The goal of this project is to explore how fouling affects a team's overall outcome in the First Robotics Competition. While fouling incurs a penalty on the offending team, the cost to the receiving team is unknown. This project aims to determine if there is a measurable advantage or disadvantage to fouling in relation to winning.

### Data:

Describe the source of the data.  Where it comes from, any relevant fields.

### Exploratory data analysis:

Insert exploratory data analysis here...

  Describe what you did.

  Include at least 3 different graphs or tables.  
```{r}
blueWinnerDetails <- rename(select(subset(matchdetails, matchdetails$winning_alliance == "blue"), 
                               "winning_alliance",
                               "alliances.blue.score"),
                            WinningScore = alliances.blue.score)
redWinnerDetails <- rename(select(subset(matchdetails, matchdetails$winning_alliance == "red"), 
                                  "winning_alliance",
                                  "alliances.red.score"),
                           WinningScore = alliances.red.score)

winnerDetails <- rbind(redWinnerDetails, blueWinnerDetails)

g <- ggplot(winnerDetails, aes(x = winning_alliance, y = WinningScore, color = winning_alliance))
g + geom_boxplot()

```

### Inference/Modeling:

#### Hypothesis:
Frame your question in terms of a hypothesis test or regression problem.

#### Findings:
Use R to conduct the experiment and show the outcome.
```{r}

```
### Conclusion:

Insert conclusion here...

### References:

Insert references here...

### Appendix:

Insert appendix here...